Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-24 numerical-amr.tex
Added one more refinement method (which Sam Skillmin *promises* me will be put into enzo-dev before the paper appears on the arXiv).

>>>>

\item{\em Second Derivative.}  This is similar to the refinement criteria used
  in Paramesh and was originally developed by \cite{1987nasa.reptQ....L}.  This
  method calculates the second derivative of a user-defined field normalized by
  the first derivative, and sets a threshold for refinement.  More background
  information can be found in the FLASH4 user guide\footnote{\url{http://flash.uchicago.edu/site/flashcode/user\_support/flash4\_ug/}},
  but we reproduce the relevant equation here for completeness. The
  multi-dimensional version of the criteria takes in to account all
  cross-derivatives, and is expressed by

 \begin{equation}
   S = \left\{ \frac{\sum_{ij}\left( \frac{\partial^2f}{\partial x_i \partial x_j} \right)^2}{\sum_{ij}\left[ \frac{1}{2\Delta x_j}\left( \abs{\frac{\partial f}{\partial x_i}}_{x_i+\Delta x_i} + \abs{\frac{\partial f}{\partial x_i}}_{x_i-\Delta x_i} \right) + \epsilon \frac{\abs{\bar{f_{ij}}}}{\Delta x_i \Delta x_j} \right]^2} \right\}^{1/2},
   \label{eq:second-deriv_analytical}
 \end{equation}

  where $f$ is the user-defined field, $\abs{\bar{f_{ij}}}$ is an average of
  $f$ over cells in the $i$ and $j$ dimensions, and $\epsilon$ is
  a user-controlled value that provides a method of ignoring small
  fluctuations, set by default to $10^{-2}$.  If $S$ is larger than a specified
  threshold (bounded by [0,1]) a cell is marked for refinement. This threshold
  is chosen at runtime and can vary for each of the fields under consideration.
